---
title: "Format Numbers"
author: "Pep Porrà"
date: "2022-07-29"
output: git_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal

Explain different ways to format numbers

## Context

Often we want to control the way numbers are printed. Common examples are the
number of decimals of numbers in tables or include a currency with the numbers.
As always, there are multiple ways to achive this goal. We summarize many of 
the methods available here

## Format cases

We will concentrate in five format cases that can be combained among them:

1. Decimals
1. Lengths
1. Units
1. Prefix
1. Percentage

### Decimals

```{r}
# example
n_ex<-  c(pi, 0.01, 2345.6789, 10000, 1/3)
n_ex
```

Numbers are printed using default options in R:

```{r}
all_options <- options()
```

```{r}
all_options$digits
```
```{r}
all_options$scipen
```

```{r}
all_options$width
```
First way to get a given number of decimals is function `round()`

```{r}
round(n_ex, digits = 2)

```
```{r}
n_sci <- 100000000
n_sci
```

```{r}
round(n_sci, 2)
```

